Easy as Pi: A Network Coding Raspberry Pi Testbed

### 2016-06-06 conclusions.tex
Second pass on the conclusions

\label{sec:conclusions}
Given the need for a \ac{Raspi} testbed easy to configure and maintain
for network coding applications where results could be reproducible
in a simple fashion, we provide a testbed description at Aalborg
University with an in-depth performance evaluation for network coding
schemes to indicate the processing capabilities and energy behaviour
for two \ac{Raspi} models both of using their \ac{SIMD} capabilities
and considering a multicore implementation for the \ac{Raspi} 2. Our
findings report that processing speeds of more than X Mbps and Y Mbps are attainable for \textbf{[goodput scenarios]}, respectively, and that
processing energy per bit for network coding is below 1 nJ in a large regime
and even an order of magnitude lower for some algorithms with the same power consumption for \textbf{[goodput scenarios]}. Future work in this area,
will be to evaluate further elaborated codecs, expand the setup and
automation of tasks within the testbed creation, consider other working
topologies and include a description for network connectivity where the
testbed has more autonomy with \ac{IP} address assignment.

>>>>

\label{sec:conclusions}
Given the need for low-cost, easy to configure, testbeds that enable
reproducible results, we provide a in-depth description of Aalborg
University's \ac{Raspi} testbed and how to guarantee replicable
results and managing scaling of the system.  We also provide a
performance evaluation for network coding schemes, focusing on
processing speed and energy behaviour for two \ac{Raspi} models,
including algorithms that exploit \ac{SIMD} instructions and multicore
capabilities of the \ac{Raspi} 2. Our measurements show that
processing speeds of more than 80 Mbps and 800 Mbps are attainable for
the \ac{Raspi} model 1 and 2, respectively, for a wide range of
network coding configurations and maintaining a processing energy
below 1 nJ/bit (or even an order of magnitude lower) in similar
configurations. Future work in the use of \ac{Raspi} devices will
focus on expanding the setup and automation of tasks to run the
testbed, configure specified network topologies (e.g., with specific
connectivity or packet loss ratios), reserve the use of these
sub-networks for running tailored experiments, and opening the use of
the testbed beyond our team at Aalborg University.
